CLT Results

### 2022-04-04 analysis/clt_irt_analysis.Rmd
update model comparison

@@

@@

@@

```{r}
irt1 <- add_criterion(irt1, "loo") 
irt2 <- add_criterion(irt2, "loo") 
irt3 <- add_criterion(irt3, "loo")

loo_compare(irt1, irt2, irt3)%>%as_tibble(rownames = "model")

@@

@@

```{r}
irt3_dif_sex <- add_criterion(irt3_dif_sex, "loo")

loo_compare(irt3, irt3_dif_sex)%>%as_tibble(rownames = "model")
```

@@

@@

```{r}
irt3_dif_order <- add_criterion(irt3_dif_order, "loo")

loo_compare(irt3, irt3_dif_order)%>%as_tibble(rownames = "model")
```

>>>>

irt1 <- add_criterion(irt1, "loo")

@@

irt2 <- add_criterion(irt2, "loo")

@@

irt3 <- add_criterion(irt3, "loo")

@@

```{r}
loo_compare(irt1, irt2, irt3)%>%as_tibble(rownames = "model")
```

@@

irt3_dif_sex <- add_criterion(irt3_dif_sex, "loo")

@@

```{r}
loo_compare(irt3, irt3_dif_sex)%>%as_tibble(rownames = "model")
```

@@

irt3_dif_order <- add_criterion(irt3_dif_order, "loo")

@@

```{r}
loo_compare(irt3, irt3_dif_order)%>%as_tibble(rownames = "model")
```
